Expected Dependency Pair Match:\\ Predicting improvements to {HTER} with expected syntactic structure

### 2009-05-09 mtjournal.tex
comclusion from outline

>>>>

\section{Conclusion}

expected dependency pair matching gets at something new

troubling area: speed of analysis -- current implementation requires
running a complete n-best parser

possible use: as a late-pass evaluation, to identify how systems
perform overall

future work:  explore ways to get at syntactic information without
the expense of a full parser:
\begin{itemize}
\item this work moves from an LFG parser (Owczarzak) to the
  substantially simpler and more robust Charniak system - keep going
  and look at simpler partial-parsing approaches (forests?)
\item conversely: how important is it that the parses be of
  high-quality?
\end{itemize}
